(tentative) Rotational Spectral Unmixing of Exoplanets

### 2016-09-13 paper/main.tex
new mock data based on simplified Earth surface map

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\# of Surface Types}
\label{ss:regularization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Testing with mock data}
\label{s:mockdata}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Test with idealized mock data}
\label{s:mockdata}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Creating Mock Data}
\label{ss:createmockdata}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Before applying to the observed data, we shall demonstrate the analysis procedure with a mock dataset with the known answer. 
For this purpose, we use a simplified albedo map of the Earth based on the IGBP classification. 
We re-classify the IGBP map into four surface types, ``ocean', ``vegetation', and ``soil'' and following Table 2 of \citet{Fujii2010} except that we merge ``snow'' into ``soil'' considering its small fraction. 
The upper left panel of Figure \ref{fig:mockdata} depicts such an surface classification. 
The reflectance spectra for these three surface types ($s_{kj}$) are adopted from ASTER spectral library \citep{Baldridge2009} in the same way as \citet{Fujii2010} (Figure 7 in that paper), and are shown in the upper right panel of Figure \ref{fig:mockdata}.

We then compute the geometrically weighted area fraction of each surface type (``contribution factor'' or $f^{\ast }_{ik}$) assuming an equatorial view at the quadrature \memoYF{Describe in more detail.}; this is shown in the lower left panel of Figure \ref{fig:mockdata}. 
Using $s_{kj}$ and $f^{\ast }_{ik}$, we compute the apparent albedo at each observation frame, on the assumption that the surfaces are ``Lambert'' scatterers. The effect of atmosphere is completely ignored. 
The mock lightcurves created through the above-mentioned procedure is presented in the lower right panel of Figure \ref{fig:mockdata}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!bpth]
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{IGBP_simplemap.pdf}
    \end{center}
     \end{minipage}
  \begin{minipage}{0.5\hsize}
    \begin{center}
    \includegraphics[width=\hsize]{mockdata_quadrature_bandsp.pdf}
    \end{center}
\end{minipage}
  \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_quadrature_factor.pdf}
    \end{center}
 \end{minipage}
   \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_quadrature_lc.pdf}
    \end{center}
 \end{minipage}
    \caption{Our mock data based on Earth surface. }
\label{fig:mockdata}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Testing Rotational Unmixing with Mock Data}
\label{ss:testmockdata}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
